A Privacy Aware Mobile Sensor Application

### 2015-01-30 paper.tex
conclusion added

\TODO{later.\\
* Key aspect control, can be given back to citizens via ``Privacy Dashboard''
}

>>>>

Our goal was to find a balance between the demand of the Local Authority for location-based data to improve their public services on one side, and to keep the privacy of citizens as untouched as possible on the other side.
In a structured manner we identified all actors and what kind of conflict of interests can occour. Doing this, we found potential risks and provided finally specific recommendations how to protect the citizen’s privacy. 
One central idea of these recommendations is to give the citizen as much control over their data back as possible. This can be e.g. done via a Privacy Dashboard that gives a full overview about all personal data that is stored on the system.
By implementing these privacy recommendations we found a way to satisfy the above-mentioned demand of both sides and comply with legal data protection requirements in addition.
